Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network

### 2013-08-03 doc/paper.tex
Corrected a bug in the KDE estimates that caused a decrease in measured probability near the boundaries

\begin{figure*}[t!]
\centering \includegraphics[trim=7cm 0cm 0cm 0cm,
  clip=true,scale=0.55]{9dpdf}
%\begin{array}{ccc} 
%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
%\end{array}$
\caption{\label{9dPDF} Marginalized 1D posterior probability density
  functions taken from a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS
  system.  We have plotted each of the 9 parameters for our
  non-spinning BNS problem as stated in section \ref{waveformSection}.
  Note how, even for parameters with excellent recovery, the peak of
  the 1D Gaussian is displaced from the injected value (in dashed
  red).  This is not due to a systematic bias, but is caused by the
  marginalization of a single dimension from the full 9D posterior
  space.  To better see this effect, compare the 1D PDF for
  $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in
  Figure~\ref{1414masses}.}
\end{figure*}

@@

\begin{figure*}[ht!]
  \centering \includegraphics[trim=2cm 0cm 2cm 0cm,
    clip=false,scale=0.7]{newMasses.pdf}
 \caption{Mass PDFs for the four BNS systems, averaged over each of
   the 40 injections.  The average is reported since, in practice,
   there was quantitatively no difference between the recovered PDFs
   for different systems with identical masses and SNRs.  Systems with
   identical mass ratios but different total masses have
   quantitatively identical PDFs when normalized to the total
   mass.}
  \label{metaMassPDFs}
\end{figure*}

@@

\begin{table}[b!]
\centering
\caption{68\% Credible intervals versus 1-$\sigma$ Fisher matrix uncertainties for each system in the HLV configuration.}
  \tabcolsep=0.11cm
    {\renewcommand{\arraystretch}{1.3} 
\begin{tabular}{lcccccccc}

>>>>

\begin{figure*}[t!]
\centering \includegraphics[trim=7cm 0cm 0cm 0cm,
  clip=true,scale=0.55]{9dpdf}
%\begin{array}{ccc} 
%\includegraphics[width=2.2in]{1dpdfs/mc.pdf} &\includegraphics[width=2.2in]{1dpdfs/eta.pdf}  & \includegraphics[width=2.2in]{1dpdfs/m1.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/time.pdf} &\includegraphics[width=2.2in]{1dpdfs/dist.pdf}  &\includegraphics[width=2.2in]{1dpdfs/iota.pdf}\\
%\includegraphics[width=2.2in]{1dpdfs/ra.pdf} & \includegraphics[width=2.2in]{1dpdfs/dec.pdf} & \includegraphics[width=2.2in]{1dpdfs/m2.pdf}
%\end{array}$
\caption{\label{9dPDF} Marginalized 1D  posterior probability densities
  of a typical $1.4M_{\odot}/1.4M_{\odot}$ BNS
  system.  We have plotted each of the 9 parameters for our
  non-spinning BNS problem as stated in section \ref{waveformSection}.
    Note how, even for parameters with excellent recovery, the peak of
  the 1D Gaussian is displaced from the injected value (in dashed
  red).  This is not due to a systematic bias, but is caused by the
  marginalization of a single dimension from the full 9D posterior
  space.  To better see this effect, compare the 1D PDF for
  $\mathcal{M}_{c}$ and $q$ with the 2D marginalized PDF in
  Figure~\ref{1414masses}.  The plots here represent the Gaussian kernel density
  estimator of each PDF.  The estimate for $q$ was 
  computed by reflecting the highest $10\%$ of samples across the $q=1$ boundary.  
  This was done to avoid a false decrease in estimated probability density near
  the boundary.}
\end{figure*}

@@

\begin{figure*}[ht!]
  \centering \includegraphics[trim=2cm 0cm 2cm 0cm,
    clip=false,scale=0.7]{newMasses.pdf}
 \caption{Mass PDFs for the four BNS systems, averaged over each of
   the 40 injections.  The average is reported since, in practice,
   there was quantitatively no difference between the recovered PDFs
   for different systems with identical masses and SNRs.  Systems with
   identical mass ratios but different total masses have
   quantitatively identical PDFs when normalized to the total
   mass.  Similarly to Fig. \ref{9dPDF}, we plot the Gaussian kernel density
   estimates, and reflect $10\%$ of the points across the $q = 1$ and $M_1 = M_2$ boundaries (for the three equal-mass cases).}
  \label{metaMassPDFs}
\end{figure*}

@@

\begin{table}[b!]
\centering
\caption{68\% Credible intervals versus 1-$\sigma$ Fisher matrix uncertainties for mass parameters in each system in the HLV configuration.}
  \tabcolsep=0.11cm
    {\renewcommand{\arraystretch}{1.3} 
\begin{tabular}{lcccccccc}
